### 2023-11-14 writing/manuscript.Rmd
source to data prep script
define names variables of interest

#source("../analysis/data_prep_sexdiff.R")
source("../analysis/fas.R")
source("../analysis/maha_v8c.R")

@@

>>>>

source("../analysis/data_prep_sexdiff.R")
source("../analysis/fas.R")
source("../analysis/maha_v8c.R")

@@

ability_vars <- c("cabat_ability","mdt_ability","mpt_ability")
sf_abililty_vars <- c("music_tap_n","out_of_tune_n","music_skill_n","music_listen_n")
train_vars <- c("lessons_enjoy_n","lessons_peers_n","theory_training_n","music_lessons_n")
listen_vars <- c("music_feel_n","music_listen_time_n","familiarity_tradmusic_n")
early_vars <- c("lessons_age","music_p_sing_n")
ses_vars <- c("education_n","income_n")
demog_vars <- c("gender","age")
noise_vars <- c("hearing_imp_n","workspace_n")

min.load <- 0.3 # Global threshold for factor loadings used in factor analyses
s1 <- sample(1:round(n/2)) #Subsample for exploratory analyses
s2 <- seq(1:n)[-s1] #Subsample for confirmatory analyses
